Verifying Demonstrations

### 2020-03-13 paper/intro.tex
Adds WIP contributions to intro

>>>>

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is reasonable by the results of \textcite{UWBPR}.

Second, for the assumption about sending all bits at once to hold, 
\textcite{UWBPR} requires that two devices shared a symmetric key~\(k\).
Our second contribution is \iac{PKI} and \ac{AKE} scheme for any device in 
the \ac{PKI} to convince a verifier that this is the case.
The solution relies on our first contribution.

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except \ac{DBTF} resistance.

The first (and second) contribution enables us to do \ac{DB} \ac{ABC}.
The third enables us also to do \ac{DB} \ac{ABC}, just without \ac{DBTF} 
resistance.
